ARIMA ENSEMBLE MODELS - Influenza hospitalization data

### 2025-04-25 NHSH_hospitalizations_seed_nolog_correct/ES_ARIMA/ES_ARIMA.Rmd
update

# Loads the ADJACENT states models
source("ES_ARIMA.R", local = TRUE, chdir = TRUE)

@@

```{r}
save.image("ARIMA_MODELS_influenza_hospitalization.Rdata")
```

>>>>

# Loads the ADJACENT states models
source("ES_ARIMA_nolog.R", local = TRUE, chdir = TRUE)

@@

```{r}
save.image("ARIMA_MODELS_influenza_hospitalization_nolog.Rdata")
```
